Formalizations of G\"{o}del's Ontological Proof of \\ God's Existence

### 2013-08-16 Abstract/GodProof-Abstract.tex
Improve abstract

This work attests the maturity of such automated deduction tools and 
opens new perspectives for a computer-assisted theoretical philosophy, 
where the critical discussion of the underlying 
concepts, definitions and axioms remains a human responsibility, but the computer can assist 
in building and checking rigorously correct logical arguments. And in case of 
logico-philosophical disputes, the computer can check the disputing arguments
and partially fulfill Leibniz' dictum:
Calculemus --- Let us calculate!
\end{document}

>>>>

This work attests the maturity of contemporary interactive and 
automated deduction tools and 
opens new perspectives for a computer-assisted theoretical philosophy. 
The critical discussion of the underlying 
concepts, definitions and axioms remains a human responsibility, but the computer can assist 
in building and checking rigorously correct logical arguments. In case of 
logico-philosophical disputes, the computer can check the disputing arguments
and partially fulfill Leibniz' dictum:
Calculemus --- Let us calculate!
\end{document}
